Guided Proofreading of Automatic Segmentations for Connectomics

### 2018-01-22 paper/rebuttal/CVPR2018/egrebuttal.tex

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{0125} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Rebuttal for `Guided Proofreading of Automatic Segmentations for Connectomics'}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

Thank you for your time and feedback.

\paragraph{R2: Venue} R2 writes ``While solid work, the paper is not a perfect fit for CVPR''. Biological and Cell Microscopy Image Analysis is included in the call for papers of CVPR 2018, and the field of connectomics has previously given rise to interesting papers at CVPR (Kumar et al. 2010, Kaynig et al. 2010, Jain et al. 2010, Funke et al. 2012, Pape et al. 2017). We believe our method will also be interesting to researchers working on tasks beyond connectomics, as segmentation proofreading for labeled dataset collection and correction is widely applicable in computer vision.

\paragraph{R3: U-Net training data} R3 requests further information regarding the training data of the U-Net membrane probability classifier. Section 2 of the supplemental material includes this information (supplemental material lines 140-161, Table 3). We will modify the manuscript (lines 492-493) to include a direct reference.

\paragraph{R3+R4: Network input channels} R3 is interested in seeing the performance contribution of the different input channels. R4 suggests that the membrane probabilities and the dilated border mask provide more discriminative information than the other two channels. We performed the following experiment.

\paragraph{R4: Dilated mask of the border between two segments} R4 raises the question of whether the dilated mask of the border is a crucial input to our classifier. The dilated border improves classifier performance from X accuracy to Y accuracy (Z accuracy border mask without dilation). We qualitatively describe the intention behind the border mask in lines 315-323 but will add the following table to the supplemental material.
	All experiments will be reproducible using open source code which will provide further insights into the design of our classifier.

\paragraph{R4: 2D Slices only}

\paragraph{R4: Merge error detection performance} R4 expresses concerns regarding the performance contribution of merge error correction.

\paragraph{R3: Lack of discussion regarding general semantic segmentation problems}

%{\small
%\bibliographystyle{ieee}
%\bibliography{egbib}
%}

\end{document}

### 2018-01-23 paper/rebuttal/CVPR2018/egrebuttal.tex

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,linkcolor=blue,citecolor=blue,bookmarks=false]{hyperref}

@@

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Rebuttal for `Guided Proofreading of Automatic Segmentations for Connectomics'}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

Thank you for your time and feedback.

\paragraph{R2: Venue} R2 writes ``While solid work, the paper is not a perfect fit for CVPR''. Biological and Cell Microscopy Image Analysis is included in the call for papers of CVPR 2018, and the field of connectomics has previously given rise to interesting papers at CVPR (Kumar~\etal 2010, Kaynig~\etal 2010, Jain~\etal 2010, Funke~\etal 2012, Pape~\etal 2017). %We believe our method will also be interesting to researchers working on tasks beyond connectomics, as segmentation proofreading for labeled dataset collection and correction is widely applicable in computer vision.

\paragraph{R2: Algorithmic Contribution/Innovation}

\paragraph{R2: Superhuman Accuracy on the SNEMI3D Challenge} \cite{superhuman_performance}

\paragraph{R2: Variation of Information Metric} \cite{NunezIglesias2013Machine}

\begin{figure}[h]
\begin{center}
  \includegraphics[width=\linewidth]{gfx/are_plot.pdf}
\end{center}
\vspace{-4mm}
   \caption{Adapted Rand Error distributions of novices and experts using guided proofreading (GP) and focused proofreading (FP) as part of the forced choice user experiment across slices of the AC4 subvolume.}
\label{fig:randerror}
\end{figure}

\paragraph{R2: Generalization of the AC4 Subvolume} R2 questions the generalization ability of the AC4 subvolume due to small dimensions. We agree that this dataset is small. However, it was introduced by Haehn~\etal 2014 for feasible interactive proofreading studies and is representative for the full AC4 dataset with respect to the distribution of object sizes.

@@

\paragraph{R3: U-Net training data} R3 requests further information regarding the training data of the U-Net membrane probability classifier. Section 2 of the supplemental material includes this information (supplemental material lines 140-161, Table 3). We will modify the manuscript (lines 492-493) to include a direct reference.

\paragraph{R3: Generalization to other segmentation problems} R3 misses a  discussion regarding applicability of GP to general semantic segmentation problems. We believe our method will also be interesting to researchers working on tasks beyond connectomics, as segmentation proofreading for labeled dataset collection and correction is widely applicable in computer vision. We state mandatory re-training of GP for other datasets as a limitation in the supplemental material (lines 134-138) but will further elaborate on general segmentation problems in this section.

\paragraph{R3+R4: Network input channels} R3 is interested in seeing the performance contribution of the different input channels. R4 suggests that the membrane probabilities and the dilated border mask provide more discriminative information than the other two channels. We observe that all four input channels are important to reduce VI (Table~\ref{tab:input_channels}). Similar as identified by Bogovich~\etal, image data adds intracellular structures (e.g. vesicles) to the decision process and membrane probabilities include global knowledge of the staining protocol to highlight cell membranes. We then notice, that the label channel provides knowledge about neuron shapes while the border mask covers the gap of extra-cellular space.

\begin{table}[h]
\caption{We evaluate automatic selection on the AC4 subvolume ($p_t=0.95$) using the GP classifier with different input channels and report median VI reduction. The combination of all four channels performs best.}
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
\makecell{Input channels} & \makecell{VI reduction} \\
\midrule
\emph{Image + Prob.} &  -0.094\\
\emph{Image + Prob. + Border} & -0.045\\
\emph{Image + Prob. + Label} & 0.038\\
\emph{Image + Prob. + Label + Border} & 0.065\\
\bottomrule
\end{tabular} 
}
\label{tab:input_channels}
\end{table}

\paragraph{R4: Dilated mask of the border between two segments} R4 raises the question of whether the dilated mask of the border is a crucial input to our classifier.

The dilated border improves classifier performance measured as VI reduction from $0.038$ to $0.065$ (Table~\ref{tab:input_channels}). We qualitatively describe the intention behind the border mask in lines 315-323 but will add the experiment above to the supplemental material and to the open source repository.

@@

\paragraph{R4: 2D Slices only}

\paragraph{R4: Merge error detection performance} R4 expresses concerns regarding the performance contribution of merge error correction.

{\small
\bibliographystyle{ieee}
\bibliography{../../connectomics}
}

### 2018-01-23 paper/rebuttal/CVPR2018/egrebuttal.tex

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,linkcolor=blue,citecolor=blue,bookmarks=false]{hyperref}

\newcommand{\TODO}[1]{\textcolor{green}{#1}}
\newcommand{\CHANGED}[1]{\textcolor{red}{#1}}

@@

\maketitle
\thispagestyle{empty}

Thank you for your time and feedback.

\paragraph{R2: Venue} R2 writes ``While solid work, the paper is not a perfect fit for CVPR''. Biological and Cell Microscopy Image Analysis is included in the call for papers of CVPR 2018, and the field of connectomics has previously given rise to interesting papers at CVPR (Kumar~\etal 2010, Kaynig~\etal 2010, Jain~\etal 2010, Funke~\etal 2012, Pape~\etal 2017). %We believe our method will also be interesting to researchers working on tasks beyond connectomics, as segmentation proofreading for labeled dataset collection and correction is widely applicable in computer vision.

\paragraph{R2: Algorithmic Contribution/Innovation} R2 finds that the algorithmic contribution of our work is limited and less innovative. While we use a traditional CNN architecture, the GP framework can work with many classifiers and we believe is a promising direction to proofread segmentations more efficiently (lines 145-151).

\paragraph{R2: Superhuman Accuracy on the SNEMI3D Challenge} R2 misses the comparison to Lee~\etal~\cite{superhuman_performance} and asks whether proofreading is still competitive. Lee~\etal indeed report fantastic performance with their segmentation method but they also state the need for proofreading as future directions~\cite[sec. 8.2]{superhuman_performance}. We will integrate this discussion into the manuscript.

\paragraph{R2: Variation of Information Metric} R2 wishes to see the results reported using the adapted Rand Error metric (aRE). We originally chose variation of information (VI) to overcome some previously reported limitations of aRE \cite[p. 5]{NunezIglesias2013Machine} but will include aRE numbers as part of the supplemental material as reported in Table~\ref{tab:randerror}.

%\begin{figure}[h]
%\begin{center}
%  \includegraphics[width=\linewidth]{gfx/are_plot.pdf}
%\end{center}
%\vspace{-4mm}
%   \caption{Adapted Rand Error distributions of novices and experts using guided proofreading (GP) and focused proofreading (FP) as part of the forced choice user experiment across slices of the AC4 subvolume.}
%\label{fig:randerror}
%\end{figure}
\begin{table}[h]
\caption{The results of the Forced Choice User Experiment reported using the adapted Rand Error (aRE) metric, the lower the better. Novices and experts using GP perform better than using FP.}
\resizebox{\linewidth}{!}{
\begin{tabular}{lcccccccccc}
\toprule
% & \multicolumn{10}{c}{adapted Rand Error (aRE) per AC4 Subvolume slice} \\
% \midrule
Slice & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
\midrule
\emph{Init. Segm.} & 0.074 & 0.081 & 0.085 & 0.079 & 0.103 & 0.098 & 0.176 & 0.188 & 0.206 & 0.174 \\
\midrule
\emph{FP Novices} & 0.073 & 0.082 & 0.086 & 0.091 & 0.102 & 0.103 & 0.182 & 0.184 & 0.209 & 0.167 \\
\emph{GP Novices} & 0.054 & 0.074 & 0.083 & 0.081 & 0.100 & 0.086 & 0.127 & 0.095 & 0.100 & 0.096 \\
\midrule
\emph{FP Experts} & 0.066 & 0.080 & 0.078 & 0.087 & 0.083 & 0.096 & 0.163 & 0.174 & 0.202 & 0.155 \\
\emph{GP Experts} & 0.051 & 0.074 & 0.075 & 0.071 & 0.078 & 0.075 & 0.099 & 0.088 & 0.094 & 0.074 \\
\bottomrule
\end{tabular} 
}
\label{tab:randerror}
\end{table}

@@

\paragraph{R3: Generalization to other segmentation problems} R3 misses a  discussion regarding applicability of GP to general semantic segmentation problems. We believe our method will also be interesting to researchers working on tasks beyond connectomics, as segmentation proofreading for labeled dataset collection and correction is widely applicable in computer vision. We state mandatory re-training of GP for other datasets as a limitation in the supplemental material (lines 134-138) but will further elaborate on general segmentation problems in this section.

\paragraph{R3+R4: Network input channels} R3 is interested in seeing the performance contribution of the different input channels. R4 suggests that the membrane probabilities and the dilated border mask provide more discriminative information than the other two channels. We observe that all four input channels are important to reduce VI (Table~\ref{tab:input_channels}). Similar as identified by Bogovich~\etal, image data adds intracellular structures (e.g. vesicles) to the decision process and membrane probabilities include global knowledge of the staining protocol to highlight cell membranes. We then notice, that the label channel provides knowledge about neuron shapes while the border mask covers the gap of extra-cellular space.

\begin{table}[h]
\caption{We evaluate automatic selection on the AC4 subvolume ($p_t=0.95$) using the GP classifier with different input channels and report median VI reduction. The combination of all four channels performs best.}
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
\makecell{Input channels} & \makecell{VI reduction} \\
\midrule
\emph{Image + Prob.} &  -0.094\\
\emph{Image + Prob. + Border} & -0.045\\
\emph{Image + Prob. + Label} & 0.038\\
\emph{Image + Prob. + Label + Border} & 0.065\\
\bottomrule
\end{tabular} 
}
\label{tab:input_channels}
\end{table}

\paragraph{R4: Dilated mask of the border between two segments} R4 raises the question of whether the dilated mask of the border is a crucial input to our classifier. The dilated border improves classifier performance measured as VI reduction from $0.038$ to $0.065$ (Table~\ref{tab:input_channels}). We qualitatively describe the intention behind the border mask in lines 315-323 but will add the experiment above to the supplemental material and to the open source repository.

\paragraph{R4: 2D Slices only} R4 observes that GP works in 2D. We report this limitation and a proposed solution in the supplemental material lines 129-133 and will add a direct reference to the manuscript. However, 2D processing enables segmentation and proofreading in parallel to 2D image acquisition prior to any expensive 3D alignment.

\paragraph{R4: Merge error detection performance} R4 expresses concerns regarding the performance contribution of merge error correction. Typical connectomics segmentations begin with an over-segmentation (lines 498-499), in which we attempt to find all possible cell boundary edges. At this stage, some edges are missed due to low contrast - these missing edges cause merge errors. To correct this, we need to imagine where any number of edges might be among empty space, and this is simply a harder visual task than assessing whether an identified edge is correct. This is true even for a human: on the AC4 dataset, our experts only agree with the selection oracle in two thirds of merge error cases.

### 2018-01-23 paper/rebuttal/CVPR2018/egrebuttal.tex

\newcommand{\TODO}[1]{\textcolor{green}{#1}}
\newcommand{\CHANGED}[1]{\textcolor{red}{#1}}
\newcommand{\JT}[1]{\textcolor{red}{[JT: #1]}}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{0125} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{\vspace{-0.5cm}Review Response for `Guided Proofreading of Automatic Segmentations for Connectomics'}  % **** Enter the paper title here

@@

\maketitle
\thispagestyle{empty}

\noindent Thank you all for your time and considered feedback.

% \emph{``While solid work, the paper is not a perfect fit for CVPR''}. 
\paragraph{R2: Venue} Biological and Cell Microscopy Image Analysis is included in the call for papers of CVPR 2018, and the field of connectomics has previously given rise to interesting papers at CVPR (Kumar~\etal 2010, Kaynig~\etal 2010, Jain~\etal 2010, Funke~\etal 2012, Pape~\etal 2017). %We believe our method will also be interesting to researchers working on tasks beyond connectomics, as segmentation proofreading for labeled dataset collection and correction is widely applicable in computer vision.

% R2 finds that the algorithmic contribution of our work is limited and less innovative. 
\paragraph{R2: Algorithmic Contribution/Innovation} While we use a traditional CNN architecture, we believe that the GP framework can work with many classifiers and is a promising direction to proofread segmentations more efficiently. % (lines 145-151).

%\paragraph{R2: Superhuman Accuracy on the SNEMI3D Challenge}
% CVPR 2018 review guidelines explicitly state: "It is Not OK to regard arXiv as a standard for the state of the art, because it is not reviewed. This applies *whoever* wrote the arXiv paper." We could push back here if you wanted
\paragraph{R2: Superhuman Performance} Lee~\etal's arXiv preprint indeed reports fantastic segmentation performance, but as a future direction they still state the need for ``guiding focused human proofreading'' with supervised learning~\cite[Sec.~8.2]{superhuman_performance}---our work is evidence to the viability of this idea. \newline \noindent \emph{``Is manual proof-reading competitive with a superhuman automatic method? Is your method able to find mistakes still present in Lee et al.'s segmentation?''} Interesting questions, to which there are no concrete answers yet (we'd be happy to test this if Lee et al.~release their software/segmentation). We can also look at this problem as one of raising the bar for manual proofreading. In their paper, Lee et al.~state that ``human accuracy depends on the procedures and software tools used to perform the reconstruction'' (Sec.~1). Through this lens, we measure by how much our software tool improves performance given consistent human time/effort across skill levels; for this, our tool advantages both novices and experts.

% These are interesting questions but how can we possibly answer them?!

\paragraph{R2: Generalization beyond the AC4 Subvolume} We agree that this dataset is small; however, it was introduced by Haehn~\etal 2014 for feasible interactive proofreading studies and is representative for the full AC4 dataset with respect to the distribution of object sizes. \JT{Evidence?}

\paragraph{R2: Rand Error} We chose variation of information (VI) to overcome previously reported limitations of aRE \cite[p.~5]{NunezIglesias2013Machine}; however, we include aRE numbers below (Table~\ref{tab:randerror}).

\begin{table}[h]
\caption{Forced Choice User Experiment in adapted Rand Error (aRE) metric (lower is better). Novices and experts using GP perform better than using FP.}
\resizebox{\linewidth}{!}{
\begin{tabular}{lcccccccccc}
\toprule
% & \multicolumn{10}{c}{adapted Rand Error (aRE) per AC4 Subvolume slice} \\
% \midrule
Slice & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
\midrule
\emph{Init. Segm.} & 0.074 & 0.081 & 0.085 & 0.079 & 0.103 & 0.098 & 0.176 & 0.188 & 0.206 & 0.174 \\
\midrule
\emph{FP Novices} & 0.073 & 0.082 & 0.086 & 0.091 & 0.102 & 0.103 & 0.182 & 0.184 & 0.209 & 0.167 \\
\emph{GP Novices} & 0.054 & 0.074 & 0.083 & 0.081 & 0.100 & 0.086 & 0.127 & 0.095 & 0.100 & 0.096 \\
\midrule
\emph{FP Experts} & 0.066 & 0.080 & 0.078 & 0.087 & 0.083 & 0.096 & 0.163 & 0.174 & 0.202 & 0.155 \\
\emph{GP Experts} & 0.051 & 0.074 & 0.075 & 0.071 & 0.078 & 0.075 & 0.099 & 0.088 & 0.094 & 0.074 \\
\bottomrule
\end{tabular} 
}
\label{tab:randerror}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% R3 requests further information regarding the training data of the U-Net membrane probability classifier. 
\paragraph{R3: U-Net training data} Section 2 of the supplemental material includes this information (supplemental material lines 140-161, Table 3). We will modify the manuscript (lines 492-493) to include a direct reference.

% R3 wishes for a discussion regarding applicability of GP to general semantic segmentation problems. 
\paragraph{R3: Generalization to other segmentation problems} We believe our method will interest researchers working beyond connectomics, as segmentation proofreading for labeled dataset collection and correction is widely applicable in computer vision. We state mandatory re-training of GP for other datasets as a limitation in the supplemental material (lines 134-138) but will further elaborate on general segmentation problems in this section. \JT{Discuss.}

### 2018-01-23 paper/rebuttal/CVPR2018/egrebuttal.tex

\paragraph{R2: Generalization beyond the AC4 Subvolume} We agree that this dataset is small; however, it was introduced by Haehn~\etal 2014 for feasible interactive proofreading studies and is representative for the full AC4 dataset with respect to the distribution of object sizes. \JT{Evidence?}

\paragraph{R2: Rand Error} We chose variation of information (VI) to overcome previously reported limitations of aRE \cite[p.~5]{NunezIglesias2013Machine}; however, we include aRE numbers below (Table~\ref{tab:randerror}).

\begin{table}[h]
\caption{Forced Choice User Experiment in adapted Rand Error (aRE) metric (lower is better). Novices and experts using GP perform better than using FP.}
\resizebox{\linewidth}{!}{
\begin{tabular}{lcccccccccc}
\toprule
% & \multicolumn{10}{c}{adapted Rand Error (aRE) per AC4 Subvolume slice} \\
% \midrule
Slice & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
\midrule
\emph{Init. Segm.} & 0.074 & 0.081 & 0.085 & 0.079 & 0.103 & 0.098 & 0.176 & 0.188 & 0.206 & 0.174 \\
\midrule
\emph{FP Novices} & 0.073 & 0.082 & 0.086 & 0.091 & 0.102 & 0.103 & 0.182 & 0.184 & 0.209 & 0.167 \\
\emph{GP Novices} & 0.054 & 0.074 & 0.083 & 0.081 & 0.100 & 0.086 & 0.127 & 0.095 & 0.100 & 0.096 \\
\midrule
\emph{FP Experts} & 0.066 & 0.080 & 0.078 & 0.087 & 0.083 & 0.096 & 0.163 & 0.174 & 0.202 & 0.155 \\
\emph{GP Experts} & 0.051 & 0.074 & 0.075 & 0.071 & 0.078 & 0.075 & 0.099 & 0.088 & 0.094 & 0.074 \\
\bottomrule
\end{tabular} 
}
\label{tab:randerror}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% R3 requests further information regarding the training data of the U-Net membrane probability classifier. 
\paragraph{R3: U-Net training data} The supplemental material includes this information (lines 140--161, Table 3). We will add a direct reference to the main paper (lines 492--493).

% R3 wishes for a discussion regarding applicability of GP to general semantic segmentation problems. 
\paragraph{R3: Generalization to other segmentation problems} We believe our method will interest researchers working beyond connectomics, as segmentation proofreading for labeled dataset collection and correction is widely applicable in computer vision. We state mandatory re-training of GP for other datasets as a limitation in the supplemental material (lines 134--138) but will further elaborate on general segmentation problems in this section. \JT{Discuss.}

% R3 is interested in seeing the performance contribution of the different input channels. R4 suggests that the membrane probabilities and the dilated border mask provide more discriminative information than the other two channels. 
\paragraph{R3+R4: Input channel contributions} All four input channels help to reduce VI (Table~\ref{tab:input_channels}). As identified by Bogovich~\etal, image data adds intracellular structures (e.g., vesicles) to the decision process, and membrane probabilities include global knowledge of the staining protocol to highlight cell membranes. Then, the label channel provides knowledge about neuron shapes while the border mask covers the gap of extra-cellular space. \JT{From the table, it might make sense to test just Label+Border, because the other two decrease VI...}

\begin{table}[h]
\caption{Automatic selection on the AC4 subvolume ($p_t=0.95$) using the GP classifier with different input channels and report median VI reduction. The combination of all four channels performs best.}
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
\makecell{Input channels} & \makecell{VI reduction} \\
\midrule
\emph{Image + Prob.} &  -0.094\\
\emph{Image + Prob. + Border} & -0.045\\
\emph{Image + Prob. + Label} & 0.038\\
\emph{Image + Prob. + Label + Border} & 0.065\\
\bottomrule
\end{tabular} 
}
\label{tab:input_channels}
\end{table}

### 2018-01-23 paper/rebuttal/CVPR2018/egrebuttal.tex

\begin{table}[h]
\caption{Forced Choice User Experiment in adapted Rand Error (aRE) metric (lower is better). Novices and experts using GP perform better than using FP.}
\resizebox{\linewidth}{!}{
\begin{tabular}{lcccccccccc}
\toprule
% & \multicolumn{10}{c}{adapted Rand Error (aRE) per AC4 Subvolume slice} \\
% \midrule
Slice & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
\midrule
\emph{Init. Segm.} & 0.074 & 0.081 & 0.085 & 0.079 & 0.103 & 0.098 & 0.176 & 0.188 & 0.206 & 0.174 \\
\midrule
\emph{FP Novices} & 0.073 & 0.082 & 0.086 & 0.091 & 0.102 & 0.103 & 0.182 & 0.184 & 0.209 & 0.167 \\
\emph{GP Novices} & 0.054 & 0.074 & 0.083 & 0.081 & 0.100 & 0.086 & 0.127 & 0.095 & 0.100 & 0.096 \\
\midrule
\emph{FP Experts} & 0.066 & 0.080 & 0.078 & 0.087 & 0.083 & 0.096 & 0.163 & 0.174 & 0.202 & 0.155 \\
\emph{GP Experts} & 0.051 & 0.074 & 0.075 & 0.071 & 0.078 & 0.075 & 0.099 & 0.088 & 0.094 & 0.074 \\
\bottomrule
\end{tabular} 
}
\label{tab:randerror}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% R3 requests further information regarding the training data of the U-Net membrane probability classifier. 
\paragraph{R3: U-Net training data} The supplemental material includes this information (lines 140--161, Table 3). We will add a direct reference to the main paper (lines 492--493).

% R3 wishes for a discussion regarding applicability of GP to general semantic segmentation problems. 
\paragraph{R3: Generalization to other segmentation problems} We believe our method will interest researchers working beyond connectomics, as segmentation proofreading for labeled dataset collection and correction is widely applicable in computer vision. We state mandatory re-training of GP for other datasets as a limitation in the supplemental material (lines 134--138) but will further elaborate on general segmentation problems in this section. \JT{Discuss.}

% R3 is interested in seeing the performance contribution of the different input channels. R4 suggests that the membrane probabilities and the dilated border mask provide more discriminative information than the other two channels. 
\paragraph{R3+R4: Input channel contributions} All four input channels help to reduce VI (Table~\ref{tab:input_channels}). As identified by Bogovich~\etal, image data adds intracellular structures (e.g., vesicles) to the decision process, and membrane probabilities include global knowledge of the staining protocol to highlight cell membranes. Then, the label channel provides knowledge about neuron shapes while the dilated mask of the border covers the gap of extra-cellular space. \newline \noindent \textbf{R4:} Adding the dilated mask of the border decreases VI. \JT{From the table, it might make sense to test just Label+Border, because the other two decrease VI...}

\begin{table}[h]
\caption{Automatic selection on the AC4 subvolume ($p_t=0.95$) using our GP classifier; median VI reduction. The combination of all four input channels performs best.}
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
\makecell{Input channels} & \makecell{VI reduction} \\
\midrule
\emph{Image + Prob.} &  -0.094\\
\emph{Image + Prob. + Border} & -0.045\\
\emph{Image + Prob. + Label} & 0.038\\
\emph{Image + Prob. + Label + Border} & 0.065\\
\bottomrule
\end{tabular} 
}
\vspace{-0.5cm}
\label{tab:input_channels}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% R4 raises the question of whether the dilated mask of the border is a crucial input to our classifier. 
%\paragraph{R4: Dilated mask of the border important?} Yes, please see Table~\ref{tab:input_channels}. We qualitatively describe the intention behind the border mask in lines 315--323 but will add the experiment above to the supplemental material and to the open source repository.

% R4 observes that GP works in 2D. 
\paragraph{R4: 2D Slices only} We report this limitation and a proposed solution in the supplemental material lines 129--133, but we will add a direct reference back in to the manuscript. 2D processing enables segmentation and proofreading in parallel to any expensive 3D alignment,

% R4 expresses concerns regarding the performance contribution of merge error correction. 
\paragraph{R4: No benefit from merge error detection?} Only in the automatic case. In the guided proofreading case, the expert is able to judge given the candidate edge we generate. That said, merge correction is simply a harder visual task than split correction. This is true even for a human: on the AC4 dataset, our experts only agree with the selection oracle in two thirds of merge error cases. For this reason, the initial over-segmentation is tuned to try to find all possible cell boundary edges, such that mostly split errors remain.

% Typical connectomics segmentations begin with an over-segmentation (lines 498--499), in which we attempt to find all possible cell boundary edges. At this stage, some edges are missed due to low contrast---these missing edges cause merge errors. To correct this, we need to imagine where any number of edges might be among empty space, and this is simply a harder visual task than assessing whether an identified edge is correct. This is true even for a human: on the AC4 dataset, our experts only agree with the selection oracle in two thirds of merge error cases.

%{\small
%\bibliographystyle{ieee}
%\bibliography{../../connectomics}
%}

### 2018-01-23 paper/rebuttal/CVPR2018/egrebuttal.tex

\noindent Thank you all for your time and considered feedback.

% \emph{``While solid work, the paper is not a perfect fit for CVPR''}. 
\paragraph{R2: Venue} Biological and Cell Microscopy Image Analysis is included in the call for papers of CVPR 2018, and the field of connectomics has previously given rise to interesting papers at CVPR (Kumar~\etal 2010, Kaynig~\etal 2010, Jain~\etal 2010, Funke~\etal 2012, Pape~\etal 2017). %We believe our method will also be interesting to researchers working on tasks beyond connectomics, as segmentation proofreading for labeled dataset collection and correction is widely applicable in computer vision.

% R2 finds that the algorithmic contribution of our work is limited and less innovative. 
\paragraph{R2: Algorithmic Contribution/Innovation} While we use a traditional CNN architecture, we believe that the GP framework can work with many classifiers and is a promising direction to proofread segmentations more efficiently. % (lines 145-151).

%\paragraph{R2: Superhuman Accuracy on the SNEMI3D Challenge}
% CVPR 2018 review guidelines explicitly state: "It is Not OK to regard arXiv as a standard for the state of the art, because it is not reviewed. This applies *whoever* wrote the arXiv paper." We could push back here if you wanted
\paragraph{R2: Superhuman Performance} Lee~\etal's arXiv preprint indeed reports fantastic segmentation performance, but as a future direction they still state the need for ``guiding focused human proofreading'' with supervised learning~(Sec.~8.2)---our work is evidence that this idea is viable. \newline \noindent \emph{``Is manual proof-reading competitive with a superhuman automatic method? Is your method able to find mistakes still present in Lee et al.'s segmentation?''} Interesting questions, to which there are no concrete answers yet (we'd be happy to test this if Lee et al.~release their software/segmentation). We can also look at this problem as one of raising the bar for manual proofreading. In their paper, Lee et al.~state that ``human accuracy depends on the procedures and software tools used to perform the reconstruction'' (Sec.~1). Through this lens, we measure by how much our software tool improves performance given consistent human time/effort across skill levels; for this, our tool advantages both novices and experts.

### 2018-03-08 paper/conclusion.tex
Update final version of paper and supplemental.

Manual proofreading of connectomics segmentations is necessary, but it is a time consuming and error-prone task. We attempt to minimize manual labor and reduce the human bottleneck. Our classifiers can detect errors and suggest potential corrections to automatically improve segmentations, but performance can increase with guided human attention. Our approach makes it easier for both novices and experts to proofread successfully, and is significantly better than the existing baseline at this task. This helps reduce the human time spent finding and correcting errors, and so makes it faster to generate new ground truth label data. We provide our framework and data as free and open research at (source/data URL omitted for review).%\url{http://rhoana.org/guidedproofreading/}.

@@

%\section*{Acknowledgements}
%We would like to thank Stephen Plaza for detailed explanations of focused proofreading and Toufiq Parag for the configuration of the NeuroProof classifier.

>>>>

Manual proofreading of connectomics segmentations is necessary, but it is a time consuming and error-prone task. We attempt to minimize manual labor and reduce the human bottleneck. Our classifiers can detect errors and suggest potential corrections to automatically improve segmentations, but performance can increase with guided human attention. Our approach makes it easier for both novices and experts to proofread successfully, and is significantly better than the existing baseline at this task. This helps reduce the human time spent finding and correcting errors, and so makes it faster to generate new ground truth label data. We provide our framework and data as free and open research at \url{http://rhoana.org/guidedproofreading/}.

@@

\section*{Acknowledgements}
We would like to thank Stephen Plaza for detailed explanations of \emph{Focused proofreading} and Toufiq Parag for the configuration of the \emph{NeuroProof} classifier. This research is supported in part by NSF grants IIS-1447344 and IIS-1607800, by the Intelligence Advanced Research Projects Activity (IARPA) via Department of Interior/Interior Business Center (DoI/IBC) contract number D16PC00002, and by the King Abdullah University of Science and Technology (KAUST) under Award No. OSR-2015-CCF-2533-01.
